Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-20 papers/ms.tex
update ms

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the left-panel of Figure~\ref{fig:lithium}, while still
being above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$).
The right panel shows the comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

One explanation for this could be that Kepler-1643 is a field
interloper; another could be that RSG-5 is older than 50\,Myr.  We do
not favor the former, given that {\it i)} the star was selected based
on its spatio-kinematic proximity to other RSG-5 members, nearly all
of which appear consistent with being $\approx$50\,Myr old
(Figure~\ref{fig:age} upper left), and {\it ii)} the same RSG-5
members display a gyrochronal sequence consistent with being younger
than the Pleaides (Figure~\ref{fig:age} lower left).  
There is a $\approx$$1\%$ chance of being a field interloper based on
the spatio-kinematic selection, and an additional low probability
($\approx1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
The extra observation of a strong lithium detection at these
effective temperatures yields a very small probability for Kepler-1643 
being a field star.
It also seems unlikely that RSG-5 could be much older than 50\,Myr,
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, as well as the data shown in rotation versus color diagram.

A third possible explanation for Kepler-1643's odd lithium equivalent
width could be tied to the calibration sample of IC\,2602 and Tuc-Hor
stars.  Analyzing Figure~\ref{fig:lithium}, it is remarkable that in
just 50 million years, stars between $4500$\,K and $5200$\,K go from
having such a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of such a dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2062 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion, which they do not.  It seems therefore that the exact
onset time of the K-dwarf lithium dispersion might be worth
clarifying.  \citet{messina_rotation-lithium_2016} for instance do not
obviously see it in the $\beta$~Pic moving group ($25\pm3$\,Myr).
Given that RSG-5 seems somewhat isochronally older than the
$\delta$~Lyr cluster (and therefore IC\,2602
\citealt{bouma_kep1627_2022}), it seems like it would be a worthy
cluster for such an analysis.

@@

As shown in Figure~\ref{fig:koiyouthindicators}, H$\alpha$ is in
emission for both components of KOI-7913, and in absorption for the
hotter stars.  Additionally, the emission appears double-peaked for
both of the KOI-7913 components.  We note that KOI-7913~A and
KOI-7913~B were spatially resolved from each other during data
acquisition.  Performing a cross-correlation between each of the stars
and the nearest matches in the Keck/HIRES template library, we also
found that the CCFs for both components of KOI-7913 showed no
indications of double-lined binarity \citep{kolbl_detection_2015}.

@@

The disposition of KOI-7913.01 has been debated: in
\texttt{q1\_q17\_dr25\_koi} the source was flagged as a false
positive, with the comment ``cent\_kic\_pos---halo\_ghost''.  This
comment and disposition were removed in the
\texttt{q1\_q17\_dr25\_sup\_koi} data release, which renamed the
planet a ``candidate''.  In this note, we discuss the interpretation
of these flags (which do not apply to the system, according to the
latest analysis).  We also discuss how the relative locations of
KOI-7913~A and KOI-7913~B affect the interpretation of the Kepler
data.

@@

Given the orientation of the stars and the $\approx$1.5 pixel FWHM of
the Kepler pixel response function, some blending between the two
stars is present.  The pointing geometries from quarters 3, 7, 11, and
15 however did not noticeably affect the observed transit depths,
which is an indication that the crowding metric applied in the data
products accurately correct the mean flux level
\citep{2017ksci.rept....6M}.  Analysis of the target-pixel data that
was acquired separately for KOI-7913~B also reveals a clearly
different stellar rotation period, and no hint of the transit signal.

>>>>

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the left-panel of Figure~\ref{fig:lithium}, while still
being above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA).
The right panel shows the comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

One explanation for this could be that Kepler-1643 is a field
interloper; another could be that RSG-5 is older than 50\,Myr.  We do
not favor the former, given that {\it i)} the star was selected based
on its spatio-kinematic proximity to other RSG-5 members, nearly all
of which appear consistent with being $\approx$50\,Myr old
(Figure~\ref{fig:age} upper left), and {\it ii)} the same RSG-5
members display a gyrochronal sequence consistent with being younger
than the Pleaides (Figure~\ref{fig:age} lower left).  
There is a $\approx$$1\%$ chance of being a field interloper based on
the spatio-kinematic selection, and a similar independent chance
($\approx1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
The extra observation of a strong lithium detection at these
effective temperatures yields a very small probability for Kepler-1643 
being a field interloper.
It also seems unlikely that RSG-5 could be much older than 50\,Myr,
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, as well as the data shown in rotation versus color diagram.

A third possible explanation for Kepler-1643's odd lithium equivalent
width could be tied to the calibration sample of IC\,2602 and Tuc-Hor
stars.  Analyzing Figure~\ref{fig:lithium}, it is remarkable that in
just 50 million years, stars between $4500$\,K and $5200$\,K go from
having such a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2062 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion, which they do not.  It seems therefore that the exact
onset time of the K-dwarf lithium dispersion might be worth
clarifying.  \citet{messina_rotation-lithium_2016} for instance do not
obviously see it in the $\beta$~Pic moving group ($25\pm3$\,Myr).
Given that RSG-5 seems somewhat isochronally older than the
$\delta$~Lyr cluster (and therefore IC\,2602;
\citealt{bouma_kep1627_2022}), it seems like it would be a worthy
cluster for such an analysis.

@@

As shown in Figure~\ref{fig:koiyouthindicators}, H$\alpha$ is in
emission for both components of KOI-7913, and in absorption for the
hotter stars.  Additionally, the emission appears double-peaked for
both of the KOI-7913 components.  An important note is that KOI-7913~A and
KOI-7913~B were spatially resolved from each other during data
acquisition.  Performing a cross-correlation between each of the stars
and the nearest matches in the Keck/HIRES template library, we also
found that the CCFs for both components of KOI-7913 showed no
indications of double-lined binarity \citep{kolbl_detection_2015}.

@@

The disposition of KOI-7913.01 has been debated: in
\texttt{q1\_q17\_dr25\_koi} the source was flagged as a false
positive, with the comment ``cent\_kic\_pos---halo\_ghost''.  This
comment and disposition were removed in the
\texttt{q1\_q17\_dr25\_sup\_koi} data release, which renamed the
planet a ``candidate''.  In this note, we discuss the interpretation
of these flags (which do not apply to the system, according to the
latest analysis).  We also discuss how the relative on-sky positions of
KOI-7913~A and KOI-7913~B affect the interpretation of the Kepler
data.

@@

Given the orientation of the stars and the $\approx$1.5 pixel FWHM of
the Kepler pixel response function, some blending between the two
stars is present.  The pointing geometries from quarters 3, 7, 11, and
15 however did not noticeably affect the observed transit depths,
which is an indication that the crowding metric applied in the data
products accurately correct the mean flux level
\citep{2017ksci.rept....6M}.  Analysis of the target-pixel data that
was separately acquired for KOI-7913~B also reveals a
different stellar rotation period, and no hint of the transit signal.
